Article title

### 2017-06-28 paper-webserver.tex
ADD: fourth para

Here we present Spfy, a platform bundling subtyping modules and machine-learning predictions for \textit{E. coli}, built using modern containerization of services, task queues for parallelizing analyses, and exception handling throughout. Spfy offers serotype predictions, identification of antimicrobial resistance genes through the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive}, and statistical or machine-learning based comparisons of groups based on user-selected restrictions. All services are publicly available at \url{https://lfz.corefacility.ca/superphy/spfy/}.

>>>>

Here we present Spfy, a platform bundling subtyping modules and machine-learning predictions for \textit{E. coli}, built using containerization of services, task queues for parallelizing analyses, and exception handling throughout. Spfy offers serotype predictions, identification of antimicrobial resistance (AMR) genes through the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive}, and statistical or machine-learning based comparisons of groups based on user-selected restrictions. All services are publicly available at \url{https://lfz.corefacility.ca/superphy/spfy/}.

Previously, we developed Superphy \cite{whiteside2016superphy} which determines Shiga toxin subtypes, AMR genes, and statistical significance tests. Spfy is a complete rewrite of Superphy integrating our Panseq \cite{laing2010pan} for pan-genome analyses of accessory genomic regions, providing long-term storage in a graph database, and containerization of services using Docker, a modern approach found in many web servers and proposed to mitigate the complexities of bioinformatic pipelines \cite{di2015impact}.
